IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-05-08 main.tex
:art: Update layout

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Received Signal}
			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
			\begin{align}
				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
			\end{align}
			capture respectively the modulated and multisine components. Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
		\end{subsection}

		\begin{subsection}{Receiving Modes}
			\begin{figure}[!t]
				\centering
				\subfloat[TS receiver\label{fi:ts_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\centering
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
								to[short,-o] ++(0,-1) node[below]{Time Switcher}
								to[short] node[spdt,anchor=in](s){} ++(0.5,0);

@@

							\draw (s.out 2) node[below right]{$\eta$}
								to ++(1.25,0)
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\\
				\subfloat[PS receiver\label{fi:ps_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){RX}(r.center)
								to[short,-o] ++(0,-1)
								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
							\draw (c.right up)
								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
								to ++(0,0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
							\draw (c.right down)
								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\caption{Practical co-located receiving modes.}
				\label{fi:receiver}
			\end{figure}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at RF-band and during RF-to-baseband conversion on tone $n$. Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms. Moreover, we define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$. Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.

@@

			\begin{figure*}[!b]
				\hrule
				\begin{flalign}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).&&\label{eq:z_expand}
				\end{flalign}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{align}
			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of sine waves to the average value.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

@@

		\begin{subsection}{Active Beamforming}
			We decouple the waveform in the spatial and frequency domains by
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder. Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}^{N \times 1}$. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b_n}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
			\end{equation}

@@

			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real nonnegative and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\odot$ denotes the Hadamard product. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Received Signal}
			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)+n(t)$, where
			\begin{align}
				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
			\end{align}
			capture respectively the modulated and multisine components, and $n(t)$ is the noise at the RF-band. Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
		\end{subsection}

		\begin{subsection}{Receiving Modes}
			\begin{figure}[!t]
				\centering
				\subfloat[TS receiver\label{fi:ts_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\centering
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
								to[short,-o] ++(0,-1) node[below]{Time Switcher}
								to[short] node[spdt,anchor=in](s){} ++(0.5,0);

@@

							\draw (s.out 2) node[below right]{$\eta$}
								to ++(1.25,0)
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\\
				\subfloat[PS receiver\label{fi:ps_receiver}]{
					\resizebox{0.9\columnwidth}{!}{
						\begin{circuitikz}[transform shape]
							\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
								to[short,-o] ++(0,-1)
								to node[coupler,anchor=left up](c){Power Splitter} ++(1,0);
							\draw (c.right up)
								to[short,-o] ++(0.5,0) node[above right]{$1-\rho$}
								to ++(0,0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Information Decoder} ++(0,0);
							\draw (c.right down)
								to[short,-o] ++(0.5,0) node[below right]{$\rho$}
								to ++(0,-0.5)
								to ++(1,0)
								to node[draw,minimum height=2em,minimum width=10em,anchor=west]{Energy Harvester} ++(0,0);
						\end{circuitikz}
					}
				}
				\caption{Practical co-located receiving modes.}
				\label{fi:receiver}
			\end{figure}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$. Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:I}
				I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $I$ as the average output DC current in this paper. It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:I} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $I$ by \eqref{eq:I_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear DC terms. Moreover, we define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$. Hence, the components of $I$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.

@@

			\begin{figure*}[!b]
				\hrule
				\begin{align}
					&I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:I_expand}\\
					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
					&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
					&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
					&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				\mathcal{C}_{\mathrm{R-E}}
				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le I,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{align}
			where $P$ is the average transmit power budget and \num{1/2} converts the peak value of sine waves to the average value.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{I(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

@@

		\begin{subsection}{Active Beamforming}
			We decouple the waveform in the spatial and frequency domains by
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n}
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder. Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b_n}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
			\end{equation}

@@

			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:I_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $I \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.
